### 2017-08-07 README.Rmd
clean up readme

> Nonparametric variable importance analysis for the assessment of differential
> methylation

@@

Note about shrinkage of influence curves, adapting @smyth2004linear.

More exposition here....

@@

## Example

@@

```{r example}
## basic example code
```

>>>>

> Targeted learning of variable importance measures for the analysis of
> differential methylation experiments

@@

<!--
Note about shrinkage of influence curves, adapting @smyth2004linear.

More exposition here....
-->

@@

<!--
## Example

@@

```{r example}
## basic example code
```
-->
